---
title: "Turba Type Statistical Comparison - Ruby with Kar"
author: "Kar"
date: "2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 R libraries

```{r, warning=FALSE}
library(tidyverse)

```

# 2 Data import

```{r}
dataset <-read_csv("Dataset.csv") 

```

# 3 Data manipulation

```{r}
dataset2 <- dataset %>% 
  select(-Size, -Plant, -Treatment) %>% 
  mutate(Type = as.factor(Type))

summary(dataset2)

```

# 4 Graph

```{r, fig.width=8, fig.height=8}
# Set df
graph_data <- dataset2 %>% 
  pivot_longer(c(2:10), 
               names_to = "parameter",
               values_to = "result")

# x label for sample size

graph_data <- graph_data %>% 
  group_by(Type, parameter) %>% 
  mutate(count = n(),
         x_label = paste(Type, "\n", "(n = ", count, ")")) 


# graph

ggplot(graph_data, aes(x = x_label, y = result, fill = Type)) +
  geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(fill = Type), shape = 21, alpha = 0.5) +
  facet_wrap(~parameter, scale = "free") +
  theme_classic() +
  theme(legend.position = "none") 
  

```

# 5 Statistical comparison

## 5.1 pH Comparison

*Model building*

```{r}
# set up df

ph_data <- dataset2[, 1:2]

# ANOVA model

ph_model <- aov(pH ~ Type, data = ph_data)
summary(ph_model)

```

**Assumption test**

* *Normality test*

Using Shapiro-Wilk test to test for normality of individual groups. Ho is normalily distributed. All three groups have to be having p-value of higher than 0.05.

```{r}
by(ph_data$pH, ph_data$Type, shapiro.test)

```

* *Levene test*

Apply levene test to find out are groups having equal variances. Ho = equal variances.
* Result shows that groups have having unequal variances (P-value < 0.05). 

```{r}
library(DescTools)   # To use Levene test

LeveneTest(ph_data$pH ~ ph_data$Type)

```

**Apply Kruskal-Wallies**

Assumptions of ANOVA are violiated, and therefore Kruskal-wallies is selected as the non-parametric omnibus test to find out whether there is significant differences between groups.

```{r}
kruskal <- kruskal.test(ph_data$pH ~ ph_data$Type)

kruskal$p.value

```
**Pos-hoc: Dunn's test **

Dunn.s test is selected as the post hoc test.

```{r}
library(dunn.test)
dunn.test(ph_data$pH, ph_data$Type, method = "bonferroni")

```


```{r}
library(DescTools)
DunnTest(ph_data$pH~ph_data$Type)

```


